Post MCMCglmm analyses

### 2021-04-08 Analysis/06-post_mcmcglmm_analyses.Rmd
expectations

>>>>

We can then measure different stuff from these ellipses (e.g. going full statistics from Robinson & Beckerman).

However, here I'm just going to focus on the elaboration/exploration of these ellipses. For the three clades, I'm going to measure:
 * the angle of the clade's ellipse to the general one (which will be their degree of exploration);
 * their scaled projection (where the ellipses all start from the point 0,0): showing how much the clade elaborates on the major phylo axis;
 * and their scaled rejection (how much they explore).

For these three metrics I expect:
 * the gulls and plovers to elaborate quiet a lot (angle ~90) compared to the sandpipers (angle ~90)
 * the gulls to explore the more followed by the plovers and then the sandpipers
 * the sandpipers to ellaborate the more followed by the gulls and then the plovers

Note that the three metrics are measured independently of the ellipse position in space and are measured in 3D.

```{r}

```
